Holomorphic field theories and higher algebra

### 2024-09-17 draft.tex
added subsections on fermionic theories and sigma models

This example admits a natural generalization to an arbitrary complex manifold.
The input data is a complex manifold $X$ of arbitrary complex dimension $n$, 
together with a holomorphic vector bundle $V$ on~$X$.
(Above we took this bundle to be trivial.)
The fields of the theory consist of a pair $(\gamma,\beta)$ where 
\[
\gamma \in \Gamma(X,V) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(X,V^*) .
\]
The action functional is 
\[
\int_X \beta \wedge \dbar \gamma
\]
and the equations of motion are
\[
\dbar \gamma = 0 = \dbar \beta.
\]
We again suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.

We will not examine fermions here,
but note that it is straightforward to consider super-holomorphic vector bundles,
i.e., holomorphic $\ZZ/2$-graded vector bundles.
In this way, one can develop analogs of fermions.

@@

\owen{Quickly explain the nonlinear analog of the $\beta\gamma$ system.}

>>>>

This example admits a natural generalization to an arbitrary complex manifold.
The input data is a complex manifold $X$ of arbitrary complex dimension $n$, 
together with a holomorphic vector bundle $V$ on~$X$.
(Above we took this bundle to be trivial.)
Each field of the theory consists of a pair $(\gamma,\beta)$ where 
\[
\gamma \in \Gamma(X,V) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(X,V^*) .
\]
The action functional is 
\[
\int_X \beta \wedge \dbar \gamma
\]
and the equations of motion are
\[
\dbar \gamma = 0 = \dbar \beta.
\]
Solutions consist of a holomorphic function $\gamma$ and a holomorphic $(n,n-1)$-form.
We again suggest to identify solutions to the second equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.

\subsubsection{Holomorphic fermions}

It is straightforward to modify the example above to allow super-holomorphic vector bundles,
i.e., holomorphic $\ZZ/2$-graded vector bundles.

For example, given a holomorphic vector bundle $V$ on a complex $n$-fold~$X$,
let $\Pi V$ denote the parity-reversed vector bundle,
i.e., we now give $V$ an odd grading.
There is a $bc$ system that is the fermionic analog of the $\beta\gamma$ system.
The fields of the theory consist of a pair $(c,b)$ where 
\[
c \in \Gamma(X,\Pi V) \quad\text{and}\quad b \in \Omega^{n,n-1}(X,\Pi V^*) .
\]
Thus, $b$ and $c$ are fermionic fields.
The action functional is 
\[
\int_X b \wedge \dbar c,
\]
and the equations of motion are
\[
\dbar c = 0 = \dbar c.
\]
We again suggest to identify solutions to the equation $\dbar c = 0$ that differ by a $\dbar$-exact form.

There is a special class of fermionic theories that is quite interesting.
Let $X$ be a complex $n$-fold where
\begin{itemize}
\item $n = 2k+1$ is odd and
\item there is a line bundle $L \to X$ such that $L^{\otimes 2} \cong K_X$,
i.e., $L$ is a square root of the canonical bundle.
\end{itemize}
A field is a section
\[
\psi \in \Omega^{0,k}(X,\Pi L),
\]
the action functional is
\[ 
\int_X \psi \wedge \dbar \psi,
\]
and the equation of motion is
\[
\dbar \psi = 0.
\]
We suggest to identify solutions that differ by $\dbar$-exact terms.

From the point of view of derived geometry, the cochain complex
\[
\Omega^{0,\bullet}(X, \Pi L)[k]
\]
presents a derived stack that should be viewed as the moduli of solutions for this theory.

\owen{What do you think of this example?}

@@

A $\sigma$-model is a field theory whose space of fields contains a mapping space $\Map(M,N)$.
When $N = \RR$, this mapping space simply becomes functions and so the $\sigma$-model reduces to a scalar field theory.

There is a natural generalization of the $\beta\gamma$ system to a $\sigma$ model.
Let $M$ be a complex $d$-manifold and let $N$ be a complex $n$-manifold.
The fields are a pair $(\gamma, \beta)$ where
\[
\gamma \in \Map(M,N) \quad\text{and}\quad \beta \in \Omega^{n,n-1}(M,\gamma^* T^*_N) .
\]
Note that $\dbar \gamma$ lives in $\Omega^{0,1}(M, \gamma^* T_N)$, 
a section of the pullback of the tangent bundle of the target.
The action functional is 
\[
\int_X \beta \wedge \dbar \gamma,
\]
where we use the canonical evaluation pairing between the pullback of the tangent and cotangent bundles of the target.
The equations of motion are
\[
\dbar \gamma = 0 = \dbar \beta,
\]
so that solutions consist of a holomorphic map $\gamma: M \to N$ and a holomorphic section $\beta$ of the pullback tangent bundle.
As usual, we suggest to identify solutions to the equation $\dbar \beta = 0$ that differ by a $\dbar$-exact form.

From derived geometry point of view, the moduli space of solutions for this $\beta\gamma$-system is the shifted cotangent bundle\owen{supervise notation!}
\[
T^*[-1] \Map_\dbar(M,N) 
\]
a rather natural space to study in complex geometry.
